---
title: "02_query_surveys_and_save_to_csv"
format: html
editor: visual
---

## About

This notebook saves cohorts from relevant AllOfUs surveys to CSVs, so they can be analyzed/accessed on the Researcher Workbench directly from cloud storage without incurring more query costs. CSV files must be created and analyzed in the AllOfUs Researcher Workbench environment (Registered tier)

Code below was entirely generated by the AllOfUs dataset builder automatically except for minor renaming changes where indicated (note starting with `# OE Note.`).

Dataset used: All of Us Registered Tier Dataset v7

## Setup

```{r}
library(tidyverse)
library(bigrquery)
library(here)
```

## Demographic information

Note. This is stored separately from individual surveys

```{r}
demographic_data_sql <- paste(" # OE Note. Renamed for clarity
    SELECT
        person.person_id,
        person.gender_concept_id,
        p_gender_concept.concept_name as gender,
        person.birth_datetime as date_of_birth,
        person.race_concept_id,
        p_race_concept.concept_name as race,
        person.ethnicity_concept_id,
        p_ethnicity_concept.concept_name as ethnicity,
        person.sex_at_birth_concept_id,
        p_sex_at_birth_concept.concept_name as sex_at_birth
    FROM
        `person` person
    LEFT JOIN
        `concept` p_gender_concept
            ON person.gender_concept_id = p_gender_concept.concept_id
    LEFT JOIN
        `concept` p_race_concept
            ON person.race_concept_id = p_race_concept.concept_id
    LEFT JOIN
        `concept` p_ethnicity_concept
            ON person.ethnicity_concept_id = p_ethnicity_concept.concept_id
    LEFT JOIN
        `concept` p_sex_at_birth_concept
            ON person.sex_at_birth_concept_id = p_sex_at_birth_concept.concept_id
    WHERE
        person.PERSON_ID IN (SELECT
            distinct person_id
        FROM
            `cb_search_person` cb_search_person
        WHERE
            cb_search_person.person_id IN (SELECT
                person_id
            FROM
                `cb_search_person` p
            WHERE
                age_at_consent BETWEEN 65 AND 92 )
            AND cb_search_person.person_id IN (SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (1384662)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384391))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836768)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528472))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836769)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384404))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836832)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528668))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836777)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529184))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836779)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529684))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836782)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529866))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836772)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528500))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836770)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528480))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836771)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528492))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836834)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528886))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836778)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384488))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836781)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529817))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836831)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528565))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836776)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529136))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836775)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528695))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836780)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529733))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836783)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529909))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (1585806)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1585828))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836799)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529923)
                    OR  concept_id IN (836800)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529932))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836797)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529066)
                    OR  concept_id IN (836798)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529075)
                    OR  concept_id IN (1740588)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529676)
                    OR  concept_id IN (1740585)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384666))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (1585806)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1585826))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (836839)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384583))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (1384662)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384581)
                    OR  concept_id IN (1384662)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384429)
                    OR  concept_id IN (1384662)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384588))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (1585806)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1585827)
                    OR  concept_id IN (836828)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528442)
                    OR  concept_id IN (836785)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528580)
                    OR  concept_id IN (836786)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43528910)
                    OR  concept_id IN (836837)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384469)
                    OR  concept_id IN (836849)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529748)
                    OR  concept_id IN (836789)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529874)
                    OR  concept_id IN (1740677)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529918)
                    OR  concept_id IN (1740620)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384395)
                    OR  concept_id IN (1740650)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384563)
                    OR  concept_id IN (1740676)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384414)
                    OR  concept_id IN (836858)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384567)
                    OR  concept_id IN (836826)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (43529196))) criteria
            UNION
            DISTINCT SELECT
                criteria.person_id
            FROM
                (SELECT
                    DISTINCT person_id, entry_date, concept_id
                FROM
                    `cb_search_all_events`
                WHERE
                    (concept_id IN (1740671)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384402)
                    OR  concept_id IN (1740627)
                    AND is_standard = 0
                    AND  value_source_concept_id IN (1384496))) criteria ) )", sep = "")

# Formulate a Cloud Storage destination path for the data exported from BigQuery.
# NOTE: By default data exported multiple times on the same day will overwrite older copies.
#       But data exported on a different days will write to a new location so that historical
#       copies can be kept as the dataset definition is changed.
demographic_data_path <- file.path( # OE Note. Renamed for clarity
  Sys.getenv("WORKSPACE_BUCKET"),
  "bq_exports",
  Sys.getenv("OWNER_EMAIL"),
  strftime(lubridate::now(), "%Y%m%d"), # Comment out this line if you want the export to always overwrite.
  "person_91692668",
  "person_91692668_*.csv"
)
message(str_glue(
  "The data will be written to {demographic_data_path}. Use this path when reading ",
  "the data into your notebooks in the future."
))

# Perform the query and export the dataset to Cloud Storage as CSV files.
# NOTE: You only need to run `bq_table_save` once. After that, you can
#       just read data from the CSVs in Cloud Storage.
bq_table_save(
  bq_dataset_query(Sys.getenv("WORKSPACE_CDR"),
    demographic_data_sql, # OE Note. Changed to align with previous renaming
    billing = Sys.getenv("GOOGLE_PROJECT")
  ),
  demographic_data_path, # OE Note. Changed to align with previous renaming
  destination_format = "CSV"
)
```

## Survey responses

```{r}
# This query represents dataset "v28_dataset_w_concepts" for domain "survey" and was generated for All of Us Registered Tier Dataset v7
survey_data_sql <- paste(" # OE Note. Renamed for clarity
    SELECT
        answer.person_id,
        answer.survey_datetime,
        answer.survey,
        answer.question_concept_id,
        answer.question,
        answer.answer_concept_id,
        answer.answer,
        answer.survey_version_concept_id,
        answer.survey_version_name
    FROM
        `ds_survey` answer
    WHERE
        (
            answer.PERSON_ID IN (SELECT
                distinct person_id
            FROM
                `cb_search_person` cb_search_person
            WHERE
                cb_search_person.person_id IN (SELECT
                    person_id
                FROM
                    `cb_search_person` p
                WHERE
                    age_at_consent BETWEEN 65 AND 92 )
                AND cb_search_person.person_id IN (SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (1384662)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384391))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836768)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528472))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836769)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384404))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836832)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528668))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836777)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529184))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836779)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529684))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836782)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529866))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836772)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528500))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836770)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528480))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836771)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528492))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836834)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528886))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836778)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384488))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836781)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529817))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836831)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528565))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836776)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529136))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836775)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528695))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836780)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529733))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836783)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529909))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (1585806)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1585828))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836799)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529923)
                        OR  concept_id IN (836800)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529932))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836797)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529066)
                        OR  concept_id IN (836798)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529075)
                        OR  concept_id IN (1740588)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529676)
                        OR  concept_id IN (1740585)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384666))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (1585806)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1585826))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (836839)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384583))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (1384662)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384581)
                        OR  concept_id IN (1384662)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384429)
                        OR  concept_id IN (1384662)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384588))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (1585806)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1585827)
                        OR  concept_id IN (836828)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528442)
                        OR  concept_id IN (836785)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528580)
                        OR  concept_id IN (836786)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43528910)
                        OR  concept_id IN (836837)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384469)
                        OR  concept_id IN (836849)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529748)
                        OR  concept_id IN (836789)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529874)
                        OR  concept_id IN (1740677)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529918)
                        OR  concept_id IN (1740620)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384395)
                        OR  concept_id IN (1740650)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384563)
                        OR  concept_id IN (1740676)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384414)
                        OR  concept_id IN (836858)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384567)
                        OR  concept_id IN (836826)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (43529196))) criteria
                UNION
                DISTINCT SELECT
                    criteria.person_id
                FROM
                    (SELECT
                        DISTINCT person_id, entry_date, concept_id
                    FROM
                        `cb_search_all_events`
                    WHERE
                        (concept_id IN (1740671)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384402)
                        OR  concept_id IN (1740627)
                        AND is_standard = 0
                        AND  value_source_concept_id IN (1384496))) criteria ) )
            )", sep = "")

# Formulate a Cloud Storage destination path for the data exported from BigQuery.
# NOTE: By default data exported multiple times on the same day will overwrite older copies.
#       But data exported on a different days will write to a new location so that historical
#       copies can be kept as the dataset definition is changed.
survey_data_path <- file.path( # OE Note. Renamed for clarity
  Sys.getenv("WORKSPACE_BUCKET"),
  "bq_exports",
  Sys.getenv("OWNER_EMAIL"),
  strftime(lubridate::now(), "%Y%m%d"), # Comment out this line if you want the export to always overwrite.
  "survey_91692668",
  "survey_91692668_*.csv"
)
message(str_glue(
  "The data will be written to {survey_data_path}. Use this path when reading ",
  "the data into your notebooks in the future."
))

# Perform the query and export the dataset to Cloud Storage as CSV files.
# NOTE: You only need to run `bq_table_save` once. After that, you can
#       just read data from the CSVs in Cloud Storage.
bq_table_save(
  bq_dataset_query(Sys.getenv("WORKSPACE_CDR"),
    survey_data_sql, # OE Note. Changed to align with previous renaming
    billing = Sys.getenv("GOOGLE_PROJECT")
  ),
  survey_data_path, # OE Note. Changed to align with previous renaming
  destination_format = "CSV"
)
```

## Save path files, for reference

```{r}
paths_df <- rbind(
  survey_data_path,
  demographic_data_path
) |>
  as.data.frame() |>
  rename(path = V1)

paths_df_filename <- "all_survey_file_paths.csv"


# store the dataframe in current workspace
write_excel_csv(paths_df, here(paths_df_filename))

# Get the bucket name
my_bucket <- Sys.getenv("WORKSPACE_BUCKET")

# Copy the file from current workspace to the bucket
system(paste0("gsutil cp ./", paths_df_filename, " ", my_bucket, "/file_info/"), intern = TRUE)
```
