---
title: "03_aggregate_cohort"
format: html
editor: visual
---

## Setup

```{r}
library(tidyverse)
library(bigrquery)
library(googleCloudStorageR)
library(here)
```

## Helpers

Note. This function is copied from AllOfUs Researcher Workbench (there is a small set of functions made available in a Jupyter notebook to registered users).

```{r}
# Read the data directly from Cloud Storage into memory.
# NOTE: Alternatively you can `gsutil -m cp {survey_13736639_path}` to copy these files
#       to the Jupyter disk.
read_bq_export_from_workspace_bucket <- function(export_path) {
  col_types <- cols(survey = col_character(), question = col_character(), answer = col_character(), survey_version_name = col_character())
  bind_rows(
    map(
      system2("gsutil", args = c("ls", export_path), stdout = TRUE, stderr = TRUE),
      function(csv) {
        message(str_glue("Loading {csv}."))
        chunk <- read_csv(pipe(str_glue("gsutil cat {csv}")), col_types = col_types, show_col_types = FALSE)
        if (is.null(col_types)) {
          col_types <- spec(chunk)
        }
        chunk
      }
    )
  )
}
```

## Read in cohort paths

```{r}
data_paths <- read_csv(here("all_survey_file_paths.csv"))

survey_data_path <- data_paths[[1, 1]]
demographic_info_path <- data_paths[[2, 1]]
```

## Read in HCC-relevant question IDs

```{r}
hcc_to_concept_id_map <- read_csv(here("hcc_to_concept_map.csv"))
```

## Read in files

### Demographic information

```{r}
demographic_df <- read_bq_export_from_workspace_bucket(demographic_info_path)

dim(demographic_df)
```

### Survey responses

```{r}
survey_df <- read_bq_export_from_workspace_bucket(survey_data_path)

dim(survey_df)
```

## Subset survey data frames to relevant questions only

```{r}
survey_relevant_qs_df <- survey_df |>
  filter(question_concept_id %in% hcc_to_concept_id_map$value & (str_detect(answer, "- Self") | answer_concept_id %in% c(
    1384391, # HIV/AIDS
    1384581, # Hepatitis A
    1384429, # Hepatitis B
    1384588, # Hepatitis C
    1585828, # Pancreas transplant
    1585826, # Liver transplant
    1585829, # Intestine transplant
    1585824, # Heart transplant
    1585827, # Lung transplant
    1585694, # Street opioid use once or twice in past 3 months
    1585697, # Street opioid use daily in past 3 months
    1585696, # Street opioid use weekly in past 3 months
    1585695, # Street opioid use monthly in past 3 months
    1585700, # Non-medical prescription opioid use once or twice in past 3 months
    1585703, # Non-medical prescription opioid use daily in past 3 months
    1585702, # Non-medical prescription opioid use weekly in past 3 months
    1585701, # Non-medical prescription opioid use monthly in past 3 months
    1585688, # Hallucinogen use once or twice in past 3 months
    1585658, # Cocaine use once or twice in past 3 months
    1585676, # Inhalant use once or twice in past 3 months
    1585682 # Sedative use once or twice in past 3 months
  ))) # only keep health conditions respondents report having
```

## Combine with HCC to concept map

```{r}
all_relevant_qs_w_hcc_df <- survey_relevant_qs_df |>
  left_join(hcc_to_concept_id_map,
    by = c("question_concept_id" = "value"),
    relationship = "many-to-many"
  )
```

## Combine with demographic information

```{r}
all_relevant_qs_w_hcc_and_demo_df <- all_relevant_qs_w_hcc_df |>
  left_join(demographic_df, by = "person_id")
```

Verify that all respondents are aged over 65 at time of survey. This is part of the cohort building criteria so it should be the case:

```{r}
all_relevant_qs_w_hcc_and_demo_df <- all_relevant_qs_w_hcc_and_demo_df |>
  mutate(
    survey_datetime = as_datetime(survey_datetime),
    date_of_birth = as_datetime(date_of_birth),
    age_at_survey = as.numeric(survey_datetime - date_of_birth) / 365.25
  ) # dividing age in days by 365.25 to account for leap years
```

```{r}
summary(all_relevant_qs_w_hcc_and_demo_df$age_at_survey)
```

## Write to file:

```{r}
write_excel_csv(all_relevant_qs_w_hcc_and_demo_df, "aggregated_survey_responses_and_hcc_df.csv")
```
