---
title: "04_basic_eda_and_define_hcc_sets"
format: html
editor: visual
---

Note. Summary tables are generated to comply with [AllOfUs Data and Statistics Dissemination Policy](https://support.researchallofus.org/hc/en-us/articles/360043016291-How-to-comply-with-the-All-of-Us-Data-and-Statistics-Dissemination-Policy).

## Setup

```{r}
library(tidyverse)
library(here)
```

Read in data:

```{r}
survey_df <- read_csv("aggregated_survey_responses_and_hcc_df.csv")
```

Create directory to save descriptive tables and figures:

```{r}
if (!dir.exists(here("all_of_us_summary_statistics"))) {
  dir.create(here("all_of_us_summary_statistics"))
}
```

## Identify co-occurring HCC sets with > 21 respondents

Note. To comply with the All of Us Data and Statistics Dissemination Policy, this excludes all summary counts of 20 or fewer individuals as well as several co-occurring HCC sets with summary counts greater than 20.

```{r}
cooccurring_v28_hcc_counts_allofus <- survey_df |>
  group_by(person_id) |>
  summarise(hcc_set = toString(unique(hcc))) |>
  ungroup() |>
  group_by(hcc_set) |>
  summarise(
    num_respondents = length(unique(person_id)),
    respondent_ids = toString(unique(person_id))
  ) |>
  filter(num_respondents > 21)
```

Get IDs for respondents who are in sufficiently large HCC sets:

```{r}
respondent_ids <- cooccurring_v28_hcc_counts_allofus |>
  pull(respondent_ids) |>
  paste0(collapse = ", ") |>
  str_split(", ") |>
  first() |>
  as.numeric()
```

Filter survey_df to only these participants:

```{r}
survey_df <- survey_df |>
  filter(person_id %in% respondent_ids)
```

Only save co-occurring counts without IDs:

```{r}
cooccurring_v28_hcc_counts_allofus_no_ids <- cooccurring_v28_hcc_counts_allofus |>
  select(-respondent_ids)

write_csv(
  cooccurring_v28_hcc_counts_allofus_no_ids,
  here("all_of_us_summary_statistics/cooccurring_v28_hcc_counts_allofus.csv")
)
```

## Respondents by survey

```{r}
respondents_by_survey_df <- survey_df |>
  group_by(survey) |>
  summarize(num_respondents = length(unique(person_id)))

respondents_by_survey_df
```

```{r}
write_csv(
  respondents_by_survey_df,
  here("all_of_us_summary_statistics/participant_count_by_survey_df.csv")
)
```

## HCC coverage

Number of responses for each HCC-like category included:

```{r}
respondents_by_hcc_df <- survey_df |>
  group_by(hcc) |>
  summarise(num_respondents = length(unique(person_id)))

respondents_by_hcc_df
```

```{r}
write_csv(
  respondents_by_hcc_df,
  here("all_of_us_summary_statistics/participant_count_by_hcc_df.csv")
)
```

Number of HCC-relevant responses:

```{r}
hccs_by_participant_count_df <- survey_df |>
  group_by(person_id) |>
  summarise(hccs_present = length(unique(hcc))) |>
  ungroup() |>
  group_by(hccs_present) |>
  count() |>
  rename(num_respondents = n) |>
  ungroup() |>
  filter(hccs_present <= 5) # others excluded for varying reasons

hccs_by_participant_count_df
```

```{r}
write_csv(
  hccs_by_participant_count_df,
  here("all_of_us_summary_statistics/hccs_by_participant_count_df.csv")
)
```

## Respondent demographics

Age (note: this was specifically filtered for in cohort definition):

```{r}
participant_age_df <- survey_df |>
  mutate(age_at_survey = round(age_at_survey)) |>
  group_by(age_at_survey) |>
  summarise(num_respondents = n_distinct(person_id)) |>
  mutate(
    age_groups = case_when(
      age_at_survey < 70 ~ "[65-70)",
      age_at_survey < 75 ~ "[70-75)",
      age_at_survey < 80 ~ "[75-80)",
      age_at_survey < 85 ~ "[80-85)",
      .default = "[85-90)"
    )
  ) |>
  count(age_groups, wt = num_respondents, name = "respondent_count")

participant_age_df
```

```{r}
write_csv(
  participant_age_df,
  here("all_of_us_summary_statistics/participant_age_at_survey_response_df.csv")
)
```

Self-reported sex assigned at birth:

```{r}
participant_sex_at_birth_df <- survey_df |>
  group_by(sex_at_birth) |>
  summarise(num_respondents = length(unique(person_id)))

participant_sex_at_birth_df
```

```{r}
write_csv(
  participant_sex_at_birth_df,
  here("all_of_us_summary_statistics/participant_sex_at_birth_df.csv")
)
```

Self-reported race:

```{r}
participant_race_df <- survey_df |>
  group_by(race) |>
  summarise(num_respondents = length(unique(person_id)))

participant_race_df
```

```{r}
write_csv(
  participant_race_df,
  here("all_of_us_summary_statistics/participant_race_df.csv")
)
```

Self-reported ethnicity:

```{r}
participant_ethnicity_df <- survey_df |>
  group_by(ethnicity) |>
  summarise(num_respondents = length(unique(person_id)))

participant_ethnicity_df
```

```{r}
write_csv(
  participant_ethnicity_df,
  here("all_of_us_summary_statistics/participant_ethnicity_df.csv")
)
```

```{r}
# File cleanup
file.remove(here("all_survey_file_paths.csv"))
file.remove(here("hcc_to_concept_map.csv"))
file.remove(here("aggregated_survey_responses_and_hcc_df.csv"))
```
